\chapter{Introduction}\label{ch:intro}

Smart home technology has seen an exponential rate of growth over the last century.
The technology has evolved from simple home appliances, to automatic control systems for a wide range of home devices.
In particular, each iteration of new smart home technology has evolved to be more user-friendly and more integrated with the user's daily life, freeing up time for more leisure activities, while automating menial tasks.

This report will cover existing literature and the investigation into the future of smart home technology, considering computer vision and human action recognition techniques for the purpose of home automation.
Additionally, the implementation of behaviour monitoring for ambient assisted living environments is discussed with its potential for integration into predictive home control in mind.

The plan for the continuation of this thesis will be outlined with a timeline for the completion of the project, covering each of the main functions that are intended to be implemented into the demonstration environment.
The progress made during Thesis~A will be discussed, including the integration of the Kinect depth sensor with ROS 2, and the preliminary results from the test environment.

\newpage

Each chapter of the report covers the topics as follows:
\begin{itemize}
    \item Chapter~\ref{ch:lit_review} explains the background for this thesis and related research.
    \item Chapter~\ref{ch:plan} outlines the plan for Thesis~B and Thesis~C.
    \item Chapter~\ref{ch:project_prep} explains the progress that has already been made in Thesis~A, preliminary results from a test environment and the proposed technolgy stack.
    \item Chapter~\ref{ch:conclusion_future_work} summarises the report.
\end{itemize}
